---
title: ""
author: "Fanny Batista Vieira, Marcus Vinícius de Farias Barbosa e Mateus de Lima Oliveira"
date: "13 de maio de 2019"
output:
  html_document:
    code_folding: "hide"
    toc: yes
    toc_depth: 5
    toc_float:
      collapsed: no
    df_print: paged
---

## Pergunta a ser respondida: Quais departamentos quando investidos interferem no lucro das startups ?

```{r}
library(tidyverse)
options(scipen = 999)

dataset = read_csv(here::here("data/50_startups.csv"),
                 col_types = "dddcd")
```

## Análise Descritiva

### Visualização dos dados
OBS: Inserir Heatmap

```{r}
library(ggplot2)
ggplot(data = dataset) +
  geom_point(aes(x = Administration, y = Profit, color = State)) +
  facet_grid(State ~ .) +
  ggtitle('Administration Spend X Profit')

ggplot(data = dataset) +
  geom_point(aes(x = Marketing, y = Profit, color = State)) +
  facet_grid(State ~ .) +
  ggtitle('Marketing Spend X Profit')

ggplot(data = dataset) +
  geom_point(aes(x = ReD, y = Profit, color = State)) +
  facet_grid(State ~ .) +
  ggtitle('ReD Spend X Profit')

ggplot(data = dataset) +
  geom_bar(aes(State, fill = State)) +
  ggtitle('Administration X Profit')

ggplot(data = dataset) +
  geom_point(aes(x = State, y = Profit, color = State))

```

### Análise da Correlação

```{r}
cor(dataset$Administration, dataset$Profit)
cor(dataset$Marketing, dataset$Profit)
cor(dataset$ReD, dataset$Profit)
```

## Modelo de Regressão e Análise da Variância (ANOVA)

### Backward Elimination

```{r}
regressor = lm(formula = Profit ~ Administration + Marketing + ReD, data = dataset)
summary(regressor)

regressor = lm(formula = Profit ~ Administration + ReD, data = dataset)
summary(regressor)

regressor = lm(formula = Profit ~ ReD, data = dataset)
summary(regressor)
```
### ANOVA

#### Função para análise de variância
```{r}
anova(regressor)
anovaTest = aov(regressor, data = dataset)
summary(anovaTest)
```

## Análise de Resíduos

### Teste da linearidade


```{r}
predicoes = predict(regressor)
residuos = residuals(regressor)

ggplot(dataset, aes(x = ReD, y = Profit)) +
  geom_smooth(method = "lm", se = FALSE, color = "lightgrey") +     # regression line  
  geom_segment(aes(xend = ReD, yend = predicoes), alpha = .2) +     # draw line from point to line
  geom_point(aes(color = abs(residuos), size = abs(residuos))) +    # size of the points
  scale_color_continuous(low = "green", high = "red") +             # colour of the points mapped to residual size - green smaller, red larger
  guides(color = FALSE, size = FALSE) +                             # size legend removed
  geom_point(aes(y = predicoes), shape = 1) +
  theme_bw() 
```

### Teste de normalidade

```{r}
plot(regressor, which=2, col=c("red"))
```
```{r}
shapiro.test(resid(regressor))
```

The null-hypothesis of this test is that the population is normally distributed. Thus, on the one hand, if the p value is less than the chosen alpha level, then the null hypothesis is rejected and there is evidence that the data tested are not normally distributed. On the other hand, if the p value is greater than the chosen alpha level, then the null hypothesis that the data came from a normally distributed population can not be rejected (e.g., for an alpha level of .05, a data set with a p value of less than .05 rejects the null hypothesis that the data are from a normally distributed population).

### Teste da homogeinidade

```{r}
plot(regressor, which=1, col=c("blue"))  # Scale-Location Plot
```

```{r}
library(lmtest)
bptest(regressor)
```

### Teste da independência

```{r}
library(car)
durbinWatsonTest(regressor)
```

